% 01-executive-overview.tex - Executive summary of the business

\section*{Executive Overview}
This document presents an investment opportunity in Great Wall, a company with the only mission to solve the single biggest unsolved problem in cryptocurrency: the ``\$5 wrench attack.'' and the epidemic of obscurity as safety it generates.

\textbf{The problem:} \par
As self-custody becomes mainstream as captured by the trend ``Not your keys, not your coins'', users are increasingly vulnerable to physical threats and coercion.
Great Wall makes it impossible for a user to be forced, under duress, to give up their assets.

We envision a future where customers can stop hiding behind (actual) masks and proudly declare ownership of their cryptocurrency without fear.

\textbf{The solution:} \par
Our solution is a novel protocol we call \textbf{Tacit Knowledge-Based Authentication (TKBA)}. It is the first and only system designed to simultaneously satisfy four crucial security properties that, until now, have been mutually exclusive:

\begin{itemize}
    \item \textbf{Knowledge-Based (Deviceless):} Access is tied only to the user's mind (their tacit knowledge), not a physical device, seed phrase, or object that can be stolen or seized.
    \item \textbf{Individual Custody:} Upholds the core crypto promise: 'Not your keys, not your coins.' The user remains their own bank, with no reliance on third-party custodians.
    \item \textbf{Non-Obscurity:} The system's security does not rely on secret tricks. It remains 100\% secure even if the attacker knows exactly how it works (Kerckhoffs's Principle).
    \item \textbf{Coercion Resistance:} The protocol's architecture (requiring both time and tacit knowledge) makes it impossible for an attacker to gain access by force, neutralizing the \$5 wrench attack.
\end{itemize}

\textbf{Differentials:} \par
This unique combination of four properties sets Great Wall apart from all existing solutions, each of which suffers from a critical, and often dangerous, flaw.

\par\medskip\noindent
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|c|c|c|c|p{4cm}|p{4.5cm}|}
\hline
\textbf{Security Method} & \textbf{Deviceless} & \textbf{Ind. Custody} & \textbf{Non-Obscure} & \textbf{Coercion Res.} & \textbf{Existing Implementations} & \textbf{Primary Down-side} \\ \hline
\textbf{TKBA} & \textbf{\emoji{check-mark-button}} & \textbf{\emoji{check-mark-button}} & \textbf{\emoji{check-mark-button}} & \textbf{\emoji{check-mark-button}} & Great Wall. & Relies on user not forgetting their tacit knowledge (which we solve via an integrated memory coach). \\ \hline
Physical / Sharding & \emoji{cross-mark} & \emoji{check-mark-button} & \emoji{check-mark-button} & \emoji{check-mark-button} & Bank vaults, Shamir's Secret Sharing (SSS). & Astronomically high cost and operational complexity. "Glorified gold." \\ \hline
Shared / Delegated & \emoji{check-mark-button} & \emoji{cross-mark} & \emoji{check-mark-button} & \emoji{check-mark-button} & Centralized exchanges (Coinbase, Binance). & Negates the core premise of self-custody. "Not your keys..." \\ \hline
Obscurity-Based & \emoji{check-mark-button} & \emoji{check-mark-button} & \emoji{cross-mark} & \emoji{check-mark-button}* & Decoy wallets, plausible denial passphrases. & *Backfires dangerously; incentivizes more violence (torture/assassination) from an educated attacker. \\ \hline
Vanilla Self-Custody & \emoji{check-mark-button} & \emoji{check-mark-button} & \emoji{check-mark-button} & \emoji{cross-mark} & Hardware/paper wallets (Ledger, Trezor, BIP39). & Completely vulnerable to a wrench attack. \\ \hline
\end{tabular}%
}
\par\medskip

\textbf{Monetization:} \par
We are capturing this market via a high-margin subscription marketplace connecting Users (who need security) with Providers (who sell idle computation).

Our marketplace's growth is fueled by a provider-driven referral program. Providers are incentivized via affiliate commission to act as a highly-motivated, zero-base-cost sales force. They naturally recruit Users, creating a powerful and scalable growth engine that dramatically lowers our Customer Acquisition Cost (CAC).

\textbf{Swagger merchandise (Bonus):} \par
Branded apparel and accessories that build community, enhance brand loyalty, and offset CAC.
More importantly, it signals to the potential attackers that the owner is security-conscious and not an easy target.
This discourages attacks from ever starting in the first place.

We believe this will create a virtuous cycle of community pride, growth, brand loyalty, and market dominance.

\textbf{The investment opportunity:} \par
We are seeking a \$\numint{round(\seedAmount/1000,0)}K seed round to launch and scale the marketplace platform toward a \num{\targetValHigh}M valuation by Year 3.

\paragraph{Near-Term Timeline}
\begin{itemize}
  \item MVP Ready — \mvpDate
  \item First 10 Beta Clients — \betaTenDate
  \item End of Beta (50 Clients) — \betaEndDate
  \item Scale Marketing / Hire CMO — \scaleMktDate
  \item 1,000 Customers — \kCustomersDate
\end{itemize}